### 2020-04-08 Thesis-Glossary.tex
Remove \term->\ac tex alias
Work on introduction
Work on background, add demo argmap and dfd

\newcommand{\newterm}[3]{
    \newglossaryentry{#1}{
        name={#2},
        description={#3}
    }
}
\newcommand{\term}{\ac}
\newcommand{\Term}{\Ac}

@@

% Start terms
\newterm{the-cw1}{the first crypto war}{
    The flurry of evolution and conflict in encryption policy during the 1990s, characterized by episodes around export
    controls, \ac{PGP}, the \ac{clipperchip}, and early key escrow proposals
}
\newterm{the-cw2}{the second crypto war}{
    The flurry of conflict in encryption policy during the late 2010s to present, characterized by angst from the
    Snowden revelations, the proliferation of strong encryption, and the Apple vs. FBI case
}

@@

\newterm{horsemen}{the Four Horsemen}{
    Four reasons that governments and law enforcement agencies use to undercut public support for strong encryption. The
    four horsemen are terrorists, pedophiles (child pornographers), drug dealers (and traffickers), and money launderers
    (or kidnappers)
}
\newterm{horsemen-full}{The Four Horsemen of the Infocalypse}{The long name for ``The Four Horsemen''}

@@

% Start acronyms
\newabbreviation{AECA}{AECA}{Arms Export Control Act}
\newabbreviation{AV}{AV}{anti-virus}
\newabbreviation{AWA}{AWA}{All Writs Act}
\newabbreviation{CALEA}{CALEA}{Communications Assistance for Law Enforcement Act}
\newabbreviation{CFAA}{CFAA}{Computer Fraud and Abuse Act}
\newabbreviation{CP}{CP}{child pornography}
\newabbreviation{CSAM}{CSAM}{child sexual abuse material}
\newabbreviation{DE}{DE}{device encryption}
\newabbreviation{DIM}{DIM}{data in motion}
\newabbreviation{DAR}{DAR}{data at rest}
\newabbreviation{E2E}{E2E}{end to end}
\newabbreviation{E2EE}{E2EE}{end to end encryption}
\newabbreviation{EA}{EA}{exceptional access}
\newabbreviation{ECPA}{ECPA}{Electronic Communications Privacy Act}
\newabbreviation{ED}{ED}{ephemeral data}
\newabbreviation{FBI}{FBI}{Federal Bureau of Investigation}
\newabbreviation{FISA}{FISA}{Foreign Intelligence Surveillance Act}
\newabbreviation{FISAAA}{FISAAA}{FISA Amendments Act}
\newabbreviation{FISC}{FISC}{Foreign Intelligence Surveillance Court}
\newabbreviation{ITAR}{ITAR}{International Traffic in Arms Regulations}
\newabbreviation{KEK}{KEK}{key encrypting key}
\newabbreviation{LE}{LE}{law enforcement}
\newabbreviation{LEA}{LEA}{law enforcement agency}
\newabbreviation{LEO}{LEO}{law enforcement officer}
\newabbreviation{NED}{NED}{non-ephemeral data}
\newabbreviation{NSA}{NSA}{National Security Agency}
\newabbreviation{NSL}{NSL}{National Security Letter}
\newabbreviation{PAA}{PAA}{Protect America Act}
\newabbreviation{PGP}{PGP}{Pretty Good Privacy}
\newabbreviation{PIN}{PIN}{personal identification number}
\newabbreviation{PKI}{PKI}{public key infrastructure}
\newabbreviation{PW}{PW}{password}
\newabbreviation{SE}{SE}{strong encryption}
\newabbreviation{SSO}{SSO}{single sign-on}
\newabbreviation{TLS}{TLS}{Transport Layer Security}
\newabbreviation{VPN}{VPN}{virtual private network}
% End acronyms

>>>>

\newcommand{\newterm}[3]{
    \newglossaryentry{#1}{
        name={#2},
        description={#3}
    }
}

@@

% Start terms
\newterm{wicked-prob}{wicked problem}{
    A problem
}

\newterm{the-cw1}{the first crypto war}{
    The flurry of evolution and conflict in encryption policy during the 1990s, characterized by episodes around export
    controls, \ac{PGP}, the \ac{clipperchip}, and early key escrow proposals
}
\newterm{the-cw2}{the second crypto war}{
    The flurry of conflict in encryption policy during the late 2010s to present, characterized by angst from the
    Snowden revelations, the proliferation of strong encryption, and the Apple vs. FBI case
}

@@

\newterm{horsemen}{the Four Horsemen}{
    Four reasons that governments and law enforcement agencies use to undercut public support for strong encryption. The
    four horsemen are terrorists, pedophiles (child pornographers), drug dealers (and traffickers), and money launderers
    (or kidnappers)
}
\newterm{horsemen-full}{the Four Horsemen of the Infocalypse}{The long name for ``The Four Horsemen''}

@@

% Start acronyms
\newabbreviation{AECA}{AECA}{Arms Export Control Act}
\newabbreviation{AV}{AV}{anti-virus}
\newabbreviation{AWA}{AWA}{All Writs Act}
\newabbreviation{CALEA}{CALEA}{Communications Assistance for Law Enforcement Act}
\newabbreviation{CFAA}{CFAA}{Computer Fraud and Abuse Act}
\newabbreviation{CP}{CP}{child pornography}
\newabbreviation{CSAM}{CSAM}{child sexual abuse material}
\newabbreviation{CSAV}{CSAV}{computer supported argument visualization}
\newabbreviation{DE}{DE}{device encryption}
\newabbreviation{DFD}{DFD}{data flow diagram}
\newabbreviation{DIM}{DIM}{data in motion}
\newabbreviation{DAR}{DAR}{data at rest}
\newabbreviation{E2E}{E2E}{end to end}
\newabbreviation{E2EE}{E2EE}{end to end encryption}
\newabbreviation{EA}{EA}{exceptional access}
\newabbreviation{ECPA}{ECPA}{Electronic Communications Privacy Act}
\newabbreviation{ED}{ED}{ephemeral data}
\newabbreviation{FBI}{FBI}{Federal Bureau of Investigation}
\newabbreviation{FISA}{FISA}{Foreign Intelligence Surveillance Act}
\newabbreviation{FISAAA}{FISAAA}{FISA Amendments Act}
\newabbreviation{FISC}{FISC}{Foreign Intelligence Surveillance Court}
\newabbreviation{IBIS}{IBIS}{issue-based information system}
\newabbreviation{ITAR}{ITAR}{International Traffic in Arms Regulations}
\newabbreviation{KEK}{KEK}{key encrypting key}
\newabbreviation{LE}{LE}{law enforcement}
\newabbreviation{LEA}{LEA}{law enforcement agency}
\newabbreviation{LEO}{LEO}{law enforcement officer}
\newabbreviation{NED}{NED}{non-ephemeral data}
\newabbreviation{NSA}{NSA}{National Security Agency}
\newabbreviation{NSL}{NSL}{National Security Letter}
\newabbreviation{PAA}{PAA}{Protect America Act}
\newabbreviation{PGP}{PGP}{Pretty Good Privacy}
\newabbreviation{PIN}{PIN}{personal identification number}
\newabbreviation{PKI}{PKI}{public key infrastructure}
\newabbreviation{PW}{PW}{password}
\newabbreviation{SE}{SE}{strong encryption}
\newabbreviation{SSO}{SSO}{single sign-on}
\newabbreviation{TLS}{TLS}{Transport Layer Security}
\newabbreviation{VPN}{VPN}{virtual private network}
% End acronyms
